Figures and results for main manuscript

### 2020-08-04 analysis/reports/figs2.Rmd
include incl argument to test effect of less than v less than equal to

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

@@

gridExtra::grid.arrange(grobs = list(
ggplot(filter(small, !singletons, s0 > 2), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(is_fia), scales = "free_y") +
  geom_vline(xintercept = 95, color = "red", linetype = 3) +
  ggtitle("Small communities percentile: Skewness"),

ggplot(filter(small, !singletons), aes(simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(is_fia), scales = "free_y") +
  geom_vline(xintercept = 5, color = "red", linetype = 3) +
  ggtitle("Small communities percentile: Evenness")), ncol = 1)

>>>>

all_di <- read.csv(here::here("analysis", "reports", "all_di_old.csv"), stringsAsFactors = F)

@@

gridExtra::grid.arrange(grobs = list(
ggplot(filter(small, !singletons, s0 > 2, log_nparts > log(50)), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(is_fia), scales = "free_y") +
  geom_vline(xintercept = 95, color = "red", linetype = 3) +
  ggtitle("Small communities percentile: Skewness"),

ggplot(filter(small, !singletons, s0 > 2), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(is_fia), scales = "free_y") +
  geom_vline(xintercept = 95, color = "red", linetype = 3) +
  ggtitle("Small communities percentile: Skewness")#,

# 
# ggplot(filter(small, !singletons), aes(simpson_percentile)) +
#   geom_histogram(bins = 100) +
#   theme_bw() +
#   facet_wrap(vars(is_fia), scales = "free_y") +
#   geom_vline(xintercept = 5, color = "red", linetype = 3) +
#   ggtitle("Small communities percentile: Evenness")
), ncol = 1)

small %>%
  filter(s0 > 2) %>%
  group_by(is_fia) %>%
  summarize(prop_skew_high = mean(skew_percentile > 95),
            nsites = dplyr::n())

small %>%
  filter(s0 > 2, nparts > 500) %>%
  group_by(is_fia) %>%
  summarize(prop_skew_high = mean(skew_percentile > 95),
            nsites = dplyr::n())

small %>%
  group_by(is_fia) %>%
  summarize(prop_even_low = mean(simpson_percentile < 5),
            nsites = dplyr::n())

small %>%
    filter(s0 > 2, nparts > 500) %>%
  group_by(is_fia) %>%
  summarize(prop_even_low = mean(simpson_percentile < 5),
            nsites = dplyr::n())

### 2020-08-04 analysis/reports/manuscript_main.Rmd
include incl argument to test effect of less than v less than equal to

ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(7)), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("More than 1,000 parts in FS")

>>>>

ggplot(filter(fia_sized, s0 > 2, nparts >= exp(7), nparts < exp(10)), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("1,000 - 20,000 parts in FS")
